Elicitation Complexity via Convex Piecewise Linear Loss Functions

### 2018-11-10 jessie-writeup/jw-holes-carified.tex
Created file that explicitly states the parts of the proof I'm not sure how to state

\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi

@@

Let $\Y$ be a finite outcome space, with $n:=|\Y|$, and $\Delta(\Y)$ be the set of probability distributions over $\Y$.

We define the \emph{level set} of a property at report value $r\in\R$ to be the set $\Gamma_r := \{p\in\P : r \in \Gamma(p)\}$.
Additionally, we can consider an unlabeled level set $\theta$ as this same set of distributions, but not associated with the report $r$.

A set $\Theta \subseteq 2^{\Delta(\Y)}$ is an unlabeled property, and finite if $|\Theta| < \infty$.
Observe that $\Theta$ is a set of level sets, and not a function.
%\raft{Careful: $\Theta$ does not need to divide anything; $\Theta = \{\emptyset\}$ is technically an unlabeled (degenerate) property JF: Changed}

\begin{definition}
Let $\Gamma:\P\toto\R$.
Define $\text{strip}(\Gamma) := \{ \Gamma_r : r \in \R \}$.
\end{definition}
Informally, strip removes labels from the property.
\jessie{Note: Strip includes the boundaries of level sets / lower dimensional level sets.}

%\begin{notation}
%We will use the following notation: $\Gamma' = \Gamma \cap \R'$ is the property $\Gamma' : p \mapsto \Gamma(p) \cap \R'$.  
%\end{notation}

%\begin{notation}
%\jessiet{TODO: REVISIT THIS.  See Notation 3}
%  Consider two labeled properties $\gamma : \P \toto \R'$ and $\Gamma : \P \toto \R$.
%  We say $\gamma \preceq \Gamma$ if removing reports from $\Gamma$ yields $\gamma$.
%  That is, if $\gamma = \Gamma \cap \varphi(\R')$ for some injection $\varphi : \R' \to \R$.
%  Note that $\varphi(\R') \subseteq \R$.
%\end{notation}
\begin{notation}
%\jessie{Attempt 2 of the above}
Let $\gamma: \P \toto\R'$ and $\Gamma: \P \toto\R$.
We say $\gamma \preceq \Gamma$ if for all $p \in \P$, we observe $\gamma(p) \subseteq \Gamma(p)$.
\end{notation}

\begin{definition}
	\jessiet{Not sure we need this, but I feel like it might be useful in the future for showing uniqueness up to a relabeling.}
	Let $\gamma$ and $\zeta$ be set-valued properties.
	We say $\gamma~\approx~\zeta$ if $\strip(\gamma)~=~\strip(\zeta)$.
\end{definition}

Observe that for every set of properties $\gamma: \P \toto \R'$ and $\zeta: \P \toto \R$ such that $\gamma \approx \zeta$, there is a bijection $\phi:\R' \to \R$ so that $\phi(\gamma(p)) = \zeta(p)$ for all $p \in \P$.
We slightly abuse notation and, given the finite set $S$, write $\phi(S) := \{\phi(x) : x \in S \}$.
($\phi$ is real valued, but we might be taking $\phi$ on every element of a (finite?) set.)

\begin{definition}
	The elicitable property $\Gamma:\P\toto \R$ is a \emph{J-embedding} of $\gamma: \P \toto \R'$ if there exists a property $\zeta : \P \toto \R$ so that $\zeta \preceq \Gamma$ and $\gamma \approx \zeta$.
\end{definition}

%\begin{conjecture}
%Consider a nondegenerate $\gamma:\P \toto\R'$ and $\Gamma: \P \toto\R$.
%For any bijection $\phi: \R' \to \bar \R$ and property $\zeta : p \mapsto \phi(\gamma(p))$, we observe that $\gamma \preceq \Gamma \iff \zeta \preceq \Gamma$.
%\end{conjecture}
%\begin{proof}
%Assume $\gamma \preceq \Gamma$.
%Then there is an injection $\varphi: \R' \to \R$ so that $\varphi(\gamma(p)) \in \Gamma(p)$ for all $p\in \P$.
%Consider $\bar \R = \phi(\R')$, and define the injection $\bar \varphi: \bar \R \to \R$ so that $\bar \varphi: \phi(r) \mapsto \varphi(r)$. 
%
%Consider $\strip(\gamma)  = \{\Gamma_r : r \in \R' \} = \{ \Gamma_{r} : \phi(r) \in \bar \R \} = \strip(\zeta)$. 
%Therefore, $\gamma \approx \zeta$.
%Since $\zeta(p) = \phi(\gamma(p))$, we know that $\bar \varphi (\zeta(p)) = \varphi(\gamma(p))$.
%%Since $\strip(\gamma) = \strip(\zeta)$, we then know that for all $p \in \P$, that $p \in \gamma_r \iff p \in \zeta_{\phi(r)}$, and therefore $\varphi(\gamma(p)) \in \Gamma(p) \iff \bar \varphi(\zeta(p)) \in \Gamma(p)$.
%
%Thus, $\varphi(\gamma(p)) \in \Gamma(p) \iff \bar{\varphi}(\zeta(p)) \in \Gamma(p)$, so we conclude $\zeta \preceq \Gamma$.
%The other direction follows with the same logic, using $\phi^{-1}$.
%\end{proof}
%
%In this case, we say $\zeta$ is a relabeling of $\gamma$.

@@

Other notes before starting:
\begin{itemize}
%\item (Assuming the metric space is $(\Delta(\Y), \rho)$, where $\rho$ is Euclidean distance, although I don't think the choice of metric matters?).
%We just use this looking at interiors of level sets.
\item Using generalized Lebesgue measure on $\P \subset \reals^{|\Delta(\Y)|-1}$
\item The interior of a level set $X_r$ is defined as $\inter{X_r} = \{p \in X_r: \epsilon > 0,  \forall q \in B(\epsilon,p), r \in \argmin_r \E_q L(r,Y)\}$
%\item Define the boundary of the closed set $X$ by $bd(X) := X \setminus \inter{X}$.
\item A convex level set $\theta$ is \emph{full-dimensional} if it has nonempty interior. %% old: $dim(\aff(\theta)) = dim(\P)$. 
%Equivalently, $\theta$ is full-dimensional if there are distributions $p_1, p_2, \ldots, p_n \in \theta$ so that $p_1, \ldots, p_n$ are affinely independent.
%\raft{Careful; I think you need convexity here.  Probably you want to define full-dimensional as having nonempty interior, and prove this as a consequence of convexity.}
%\jessiet{What is the formal, ``universal'' definition of full-dimensional, if one exists?}
%\item A full-dimensional level set has non-empty interior.
\end{itemize}

@@

\begin{conjecture}\label{conj:gam-prime-exists}
	Let $\Gamma:\P \toto \reals^d$ be a nondegenerate elicitable property with a finite set of full-dimensional level sets $\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$.
	There exists a nondegenerate, nonredundant property $\gamma$ such that $\gamma \preceq \Gamma$. 
\end{conjecture}
\begin{proof}
\emph{Assumptions used: Finite level sets}

%	To start, construct $\R' := \{ r \in \R : \inter{\Gamma_r} \neq \emptyset \} \subseteq \R$.
%	Since $\card(\R') \leq \card(\reals^d)$, there is an injection $\varphi:\R' \to \reals^d$.
%	Observe that $\R'$ is finite and nonempty.
	Construct the finite set $\R' = \{\Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$. \jessie{TODO- Check this is how we want to construct $\R'$.}
	(If $\R'$ is not finite, choose just one $r \in \R$ so that $\theta = \Gamma_r$.)
	Defining the property $\gamma : p \mapsto \Gamma(p) \cap \R'$, we see that $\gamma \preceq \Gamma$.
	We want to show that the constructed $\gamma$ is nondegenerate and nonredundant.
	As $\Gamma$ is nondegenerate, there is some report $r \in \reals^d$ such that $r \in \Gamma(p)$.
	For every $p \in \P$, there is some level set $\theta$ so that $p \in \cl{\theta}$, and since level sets of elicitable properties are closed (see Lemma~\ref{lem:closed-level-sets}), and therefore $p \in \theta$.
	Thus there is some report $r \in \R'$ so that $r \in \gamma(p)$, so $\gamma$ is nondegenerate.
%	If $p \in \inter{\Gamma}_r$, then by construction of $\R'$, we see $r \in \R'$.
%	Since level sets are closed, for any $r \in \R'$, we know that $\varphi(r) \in \Gamma(q)$ for all $q \in bd(\Gamma_{\varphi(r)})$, and therefore there is at least one report $r \in \R'$ such that $\varphi(r) \in \Gamma(p)$ for all $p \in \P$, so $\gamma$ is nondegenerate.

	If $\gamma$ is redundant, then remove any redundant reports from $\R'$.
	Any level set with a redundant report must either (a.) equal to another level set or (b.) a proper subset of another level set. %, or (c.) span multiple level sets. %not by current definition of redundancy
	Removing redundant reports resolves (a.) and (b.).
%	As $\Gamma$ is elicitable, we can see that (c.) cannot happen.
%	First consider that any redundant report $r$ spanning multiple level sets cannot be full dimensional, as we would contradict elicitability of $\Gamma$ as the score $G$ must be convex, and therefore differentiable almost everywhere in the simplex.
%	If the level set $\Gamma_r \subseteq \Gamma_{r_1}$ or $\Gamma_{r_2}$ for $r_1$ and $r_2 \in \R'$, then we have case (b.).
%	If there is some $p \in \Gamma_r$ so that $p \not \in \Gamma_{r_1} \cap \Gamma_{r_2}$, but there is some $p \in \Gamma_{r_1} \cap \Gamma_r$ and $q \in \Gamma_{r_2} \cap \Gamma_r$, then there must be some $s \in \Gamma_r \cap \Gamma_{r_1} \cap \Gamma_{r_2}$ as the level set $\Gamma_r$ must be convex.
%	At $s$, the	subgradient set of the score $G$ is a two-dimensional closed and convex set, 
%	\jessie{... to do}

@@

%	\jessie{Skip this paragraph if you believe the last sentence by simply citing closure.}
%	Thus, we just need to show $\Gamma'(p) \neq \emptyset$ for $p \not \in \inter{\Gamma_r}$.
%	As $\Gamma$ is nondegenerate, there are then $m$ level sets $\{\Gamma_{r_i}\}_{i=1}^m$ in the $\epsilon$-ball around $p$.
%	We claim some $r_i$ is in $\R'$.
%	Since there are only a finite set of level sets, at least one in the $\epsilon$-ball centered on $p$ is full dimensional.
%	Therefore, there is some $r_i \in \R'$ so that $p \in cl(\Gamma_{r_i})$, and as level sets are closed by Lemma~\ref{lem:closed-level-sets}, we then observe $p \in \Gamma_{r_i}$.
%	Therefore $\Gamma'$ is nondegenerate.
%	\jessie{End the paragraph you can skip}

%%% COMMENTED OUT 10/19/18
%%%	Now to show $\gamma$ is nonredundant.
%%%	For contradiction, suppose $\gamma$ is redundant.
%%%	Then there are $r_1, r_2 \in \R'$ with $r_1 \neq r_2$ with full dimensional level sets $\Gamma_{r_1}$ and $\Gamma_{r_2}$ so that either $\gamma_{r_1} \subsetneq \gamma_{r_2}$ or $\gamma_{r_1} = \gamma_{r_2}$.
%%%	
%%%	\jessie{Uses a fact that requires nonredundancy to show nonredundancy... change this proof.  Or think about what it's not true.}
%%%	First, suppose $\gamma_{r_1} = \gamma_{r_2}$.
%%%	We can think as the property values as labelings of the subgradient sets (denoted by $\partial$) of the the concave Bayes Risk $G(p)$.
%%%	\jessie{Need source: Gneiting/Raftery 2007\footnote{\url{https://www.stat.washington.edu/raftery/Research/PDF/Gneiting2007jasa.pdf}} or Raf/Ian 2014\footnote{\url{http://www.cs.colorado.edu/~raf/media/papers/wine-affine.pdf}}}
%%%	As $G$ is concave, it is differentiable almost everywhere, which means that $|\partial G(p)| = 1$ almost everywhere.
%%%	Then $\gamma(p) = \partial G(p) \implies |\gamma(p)| = 1$ almost everywhere, which-- along with the fact that the level sets $\gamma_{r_1}$ and $\gamma_{r_2}$ are full dimensional (and therefore have positive measure since they are convex-- see Lemma~\ref{lem:pos-measure-iff-nonempty-int}), contradicts the claim $r_1 \neq r_2$.
%%%	Thus we conclude there aren't reports $r_1, r_2 \in \R'$ so that $r_1 \neq r_2$ and $\gamma_{r_1} = \gamma_{r_2}$.
%%%	
%%%%	By construction of $\R'$, we know both $\Gamma'_{r_1}$ and  $\Gamma'_{r_2}$ are full dimensional.
%%%%	If $\Gamma'_{r_1} = \Gamma'_{r_2} = \Gamma'_{r_1} \cap \Gamma'_{r_2}$ are full dimensional, this contradicts something?
%%%	
%%%	Otherwise suppose $\gamma_{r_1} \subsetneq \gamma_{r_2}$.
%%%	As $\gamma_{r_1}$ is full-dimensional, so is $\gamma_{r_1} \cap \gamma_{r_2} = \gamma_{r_1}$.
%%%	Again, since we know that $|\gamma(p)| = 1$ almost everywhere, and as the intersection of the two level sets is full-dimensional, this again contradicts the differentiability of $G$ almost everywhere, since the intersection of the level sets has positive measure in the simplex.
%%%	Therefore, $\gamma$ is nonredundant.
%%% END COMMENTED OUT 10/19/18
\end{proof}

\begin{lemma}\label{lem:define-trim}
	Let $\Gamma$  be a nondegenerate, elicitable property with a finite set of level sets $\Theta$ so that $\bigcup_{\theta \in \Theta} \theta = \P$.
	There exists an unlabeled property $\Theta$ so that for all nondegenerate, nonredundant $\gamma \preceq \Gamma$, we have $\strip(\gamma) = \Theta := \text{trim}(\Gamma)$.
\end{lemma}

@@

%	We just want to show $\trim(\Gamma)$ is unique because of Conjecture~\ref{conj:gam-prime-exists}.	
%	Consider two nonredundant, nondegenerate properties $\Gamma' = \Gamma \cap \R' \preceq \Gamma$ and $\tilde \Gamma  = \Gamma \cap \tilde \R \preceq \Gamma$.
%	It is sufficient to show $\Theta' := \strip(\Gamma') = \strip(\tilde \Gamma) =: \tilde \Theta$.
%	
%	First, fix a level set $\theta \in \Theta'$.
%	There is some report $r'$ so that $r' \in \Gamma(p) \cap \R'$ for all $p \in \theta$ by nondegeneracy of $\Gamma'$.
%	Now, for contradiction, suppose $\Gamma'_{r'} \not\in \strip(\tilde \Gamma)$.
%	Therefore, there is \emph{not} a report $r \in \tilde \R$ so that $\Gamma'_{r'} = \tilde \Gamma_r$.
%%	Now, if $\tilde \Gamma(p) = \emptyset$ for some $p \in \theta$, then we contradict nondegeneracy of $\tilde \Gamma$.
%	
%	As $\Gamma' \preceq \Gamma$ and $\tilde \Gamma \preceq \Gamma$, then for some $r \in \tilde \R$, we then see that either $\Gamma'_{r'} \subsetneq \tilde \Gamma_r$ or $\tilde \Gamma_r \subsetneq \Gamma'_{r'}$ since both $\Gamma'$ and $\tilde \Gamma$ are restrictions of the property $\Gamma$.
%%	(If the level sets are not equivalent, then the intersection $\Gamma'_{r'} \cap \tilde{\Gamma_r}$ must be lower dimensional by nonredundancy of $\Gamma'$ and $\tilde{\Gamma}$ since $\partial G$ is real-valued amost everywhere.)
%	The first case contradicts nonredundancy of $\Gamma'$ and the latter contradicts nonredundancy of $\tilde \Gamma$.
%	Thus, there must be some $r \in \tilde{\R}$ so that $\Gamma'_{r'} = \tilde{\Gamma_r}$, so we conclude $\Gamma'_r \in \strip(\tilde \Gamma)$.
%	
%	The other direction of inclusion follows from the same logic.
%	Therefore, for all nonredundant, non-degenerate properties $\Gamma' \preceq \Gamma$, we observe the unique unlabeled property $\trim(\Gamma) := \Theta = \strip(\Gamma')$.
%	
%	\jessie{If we think about bijections, consider the bijection $\phi: \R' \to \tilde \R$.
%	Then $\strip(\Gamma') = \{ \Gamma'_{r} : r \in \R' \} = \{ \Gamma_{\varphi(r)} : r \in \R' \} = \{ \Gamma_{\varphi(r)} : \phi(r) \in \tilde \R \} = \{ \tilde \Gamma_{\phi(r)} : \phi(r) \in \tilde \R \} = \strip(\tilde \Gamma) $, then it's simpler to state.}

@@

	In order to understand what $\trim(\Gamma)$ is, we use the property $\gamma \preceq \Gamma$ and $\R'$ constructed in Conjecture~\ref{conj:gam-prime-exists}.
	For each $\theta \in \trim(\Gamma) = \strip(\gamma)$, there must be a report $r \in \R'$ such that $\theta = \gamma_r = \Gamma_{r}$.
	By construction, $r \in \R' \implies \inter{\gamma_r} = \inter{\theta} \neq \emptyset$.
	Since $\theta$ is convex (as level sets of elicitable properties are) and has nonempty interior, then $\theta$ is full dimensional.

%	First, we see $\Theta := \trim(\Gamma) = \strip(\Gamma')$ is nonredundant in the unlabeled definition (Definition~\ref{def:unlabeled-nonredundant}) as $\Gamma'$ is nonredundant in the labeled set from Lemma~\ref{lem:nonredundant-defs-equivalent}, since we know $\Gamma'$ is well-defined and nonredundant from Conjecture~\ref{conj:gam-prime-exists}.
%	
%	
%	
%	For contradiction:
%	Let $\theta \in \Theta$ not full-dim and non-redundant (whatever that means for an unlabeled property-- see definition \ref{def:unlabeled-nonredundant} section for proposed definition).
%	
%	We now show that every level set $\theta \in \Theta = \strip(\Gamma') = \trim(\Gamma)$ is full dimensional.
%	
%	We proceed in 2 cases for a level set $\theta \in \Theta$:
%	\begin{enumerate}
%		\item For all $\theta' \in \Theta$, $\theta \cap \theta' = \emptyset$.
%		\jessie{Doesn't this only happen when $\{\theta\} = \Theta$?}
%		
%		We know the level set $\theta$ is closed by Lemma~\ref{lem:closed-level-sets}.
%		By definition of $\R'$, for $p \in \inter{\theta}$ so that for $r_\theta = \Gamma'(p)$, there is a ball $B(\epsilon, p)$ centered around $p$ so that for every $q \in B(\epsilon, p)$, $r_\theta \in \Gamma'(q)$.
%%		(In fact, as $\Theta$ is nonredundant, we claim $r_\theta = \Gamma'(q)$. \jessie{Need to show?})
%		Therefore, the level set $\Gamma_{r_\theta} = \theta$ is full dimensional as it has nonempty interior.
%		
%		Intuitively, this can be seen since the interior of $\theta$ is nonempty by nondegeneracy of $\Gamma'$.
%		
%		\bigskip
%		\hrule
%		Other notes from meeting with Raf 9/24/18:\\
%		Use closure and nondegeneracy
%		
%		Look at subset topology? ($\tau_{\R'} := \{\R' \cap U : U \in \tau \}$.)
%		
%		\hrule
%		\item There exists a level set $\theta' \in \Theta$, $\theta \cap \theta' \neq \emptyset$.
%		
%		By nonredundancy of $\Gamma'$, we then observe nonredundancy of $\Theta$, we know that $\mu(\theta \cap \theta') = 0$.
%		We want to show that $\theta$ is full dimensional.
%		
%		For contradiction, suppose $\theta \in \trim(\Gamma)$ is not full dimensional.
%		By Conjecture~\ref{conj:gam-prime-exists}, there exists a nonredundant, nondegenerate $\Gamma' \preceq \Gamma$ so that $\trim(\Gamma) = \strip(\Gamma')$.
%		Consider $\R'$ so that $\Gamma' = \Gamma \cap \R'$ as constructed in the proof of Conjecture~\ref{conj:gam-prime-exists}.
%		
%		Suppose $\theta \in \trim(\Gamma)$ is not full dimensional.
%		Then $\inter{\theta} = \emptyset$.
%		As $\trim(\Gamma) = \strip(\Gamma')$, we observe that there is a unique $r \in \R'$ so that $\Gamma'_r = \theta$.
%		However, $\inter{\theta} = \inter{\Gamma'_r} = \emptyset \implies r \not \in \R'$ by the construction of $\R'$.
%		Since $\trim(\Gamma) = \strip(\Gamma')$ \emph{for all} nonredundant, nondegenerate $\Gamma' \preceq \Gamma$-- including the $\Gamma'$ constructed in the proof of Conjecture~\ref{conj:gam-prime-exists}, then we conclude $\Gamma_r = \theta \not \in \strip(\Gamma') = \trim(\Gamma)$.
%		
%		
%		\bigskip
%		\hrule
%		Other notes from meeting:\\
%		Look at expected loss/score of $\Gamma'$.
%		\hrule
%	\end{enumerate}

%	Therefore, we have a contradiction and conclude $\theta \in \trim(\Gamma)$ is full dimensional. 
\end{proof}

\begin{conjecture}\label{conj:lev-sets-subsets}
	Let the elicitable property $\Gamma: \P \toto \reals^d$ embed the nondegenerate property $\gamma$.
	Then the level sets of $\Gamma$ are subsets of the level sets of $\gamma$.
\end{conjecture}

\begin{proof}
	\jessie{Original def of embedding}
	Showing the level sets of $\Gamma$ are subsets of the level sets of $\gamma$ is to show that $\forall r \in \reals^d$ we know $p \in \Gamma_r \implies p \in \gamma_{r'}$ for some $r' \in \R'$.
    \raf{Want to say $\forall r$ $\exists r'$ $p \in \Gamma_r \implies p \in \gamma_{r'}$.}

%	Consider $p \in \Gamma_r$.
%	Then $r \in \Gamma(p)$, and since $\Gamma$ embeds $\gamma$, we know $ r = \varphi(r') \in \gamma(p)$ and $r' \in \R'$.
%	We then know that $p \in \gamma_{r'}$.
	Consider $r_1 \in \reals^d$ and $r_2 \in \R'$.
	Suppose $q \in \Gamma_{r_1}$ but $q \not \in \gamma_{r_2}$.
	There must be no $r_2 \in \R'$ so that $\varphi(r_2) = r_1$.
	Then $q \not \in \gamma_{r_2}$ contradicts the the fact that $\Gamma$ embeds $\gamma$.
	Thus, $p \in \Gamma_{r_1} \implies \exists r_2 \in \R'$ so that $p \in \gamma_{r_2}$ .

	Therefore, every level set of the property $\Gamma$ is a subset of a level set of $\gamma$.
	\jessie{End embedding}

	\jessie{Begin J-embedding}
	Since $\Gamma$ embeds $\gamma$, there is a nondegenerate, nonredundant $\zeta: \P \toto \R$ for $\R \subseteq \reals^d$ so that $\zeta \preceq \Gamma$ and $\zeta \approx \gamma$.
	Therefore, it is sufficient to show $\theta \in \strip(\Gamma) \implies \theta \in \strip(\zeta)$.
	%Since $\zeta \preceq \Gamma$, we know for all $p \in \P$ that $\zeta(p) \subseteq \Gamma(p)$.
	Therefore, for every $r \in \reals^d$, there is some $r' \in \R$ so that $ p \in \theta = \Gamma_r = \{ p \in \P : r \in \Gamma(p) \} \subseteq \Gamma_{r'} \implies p \in \Gamma_{r'}$ since if $r \not \in \R$ it is a redundant report, so its level set is a subset or equal to another level set for a report in $\R$.
	For $r' \in \R$, we know $p \in \Gamma_{r'} \implies p \in \{ p \in \P : r' \in \Gamma(p) \cap \R \} = \{ p \in \P : r' \in \zeta(p) \} = \zeta_{r'}$. %as $\zeta(p) \subseteq \Gamma(p)$ by closure of level sets (since if a level set is lower-dimensional, there is some full-dimensional level set that it is a subset of).
	\jessie{End J-embedding}
\end{proof}

>>>>

\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\newcommand{\btw}[1]{\mytodo{gray!20!white}{BTW: #1}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi

@@

A set $\Theta \subseteq 2^{\R}$ is an unlabeled property, and finite if $|\Theta| < \infty$.
Note that $\R$ finite implies $\Theta$ is finite.
Observe that $\Theta$ is a set of level sets, and not a function.

\begin{definition}
Let $\Gamma:\P\toto\R$.
Define $\text{strip}(\Gamma) := \{ \Gamma_r : r \in \R \}$.
\end{definition}
Informally, strip removes labels from the property.
\btw{Note: Strip includes the boundaries of level sets / lower dimensional level sets.}

\begin{notation}
Let $\gamma: \P \toto\R'$ and $\Gamma: \P \toto\R$.
We say $\gamma \preceq \Gamma$ if for all $p \in \P$, we observe $\gamma(p) = \Gamma(p) \cap \R'$.
\end{notation}

\begin{definition}
	\jessie{Not sure we need this, but I feel like it might be useful in the future for showing uniqueness up to a relabeling.}
	Let $\gamma$ and $\zeta$ be set-valued properties.
	We say $\gamma~\approx~\zeta$ if $\strip(\gamma)~=~\strip(\zeta)$.
\end{definition}

Observe that for every set of properties $\gamma: \P \toto \R'$ and $\zeta: \P \toto \R$ such that $\gamma \approx \zeta$, there is a bijection $\phi:\R' \to \R$ so that $\phi(\gamma(p)) = \zeta(p)$ \footnote{Here, we slightly abuse notation and, given the finite set $S$, write $\phi(S) := \{\phi(x) : x \in S \}$.	($\phi$ is real valued, but we might be taking $\phi$ on every element of a set.)} for all $p \in \P$.

\begin{definition}
	The elicitable property $\Gamma:\P\toto \R$ is an \emph{embedding} of $\gamma: \P \toto \R'$ if there exists a property $\zeta : \P \toto \R$ so that $\zeta \preceq \Gamma$ and $\gamma \approx \zeta$.
\end{definition}

@@

\begin{definition}
	A convex level set $\theta$ is \emph{full-dimensional} if it has nonempty interior.
\end{definition}

@@

\begin{conjecture}\label{conj:gam-prime-exists}
	Let $\Gamma:\P \toto \reals^d$ be a nondegenerate elicitable property with a finite set of full-dimensional level sets $\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$.
	There exists a nondegenerate, nonredundant property $\gamma: \P \toto \R$ such that $\gamma \preceq \Gamma$. 
\end{conjecture}
\begin{proof}
\emph{Assumptions used: Finite level sets}

	Construct the finite set $\R' = \{r \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$. \jessie{(HOLE)- Check this is how we want to state the construction of $\R'$.}
	(If $\R'$ is not finite, choose just one $r \in \R$ so that $\theta = \Gamma_r$.)
	Defining the property $\gamma : p \mapsto \Gamma(p) \cap \R'$, we see that $\gamma \preceq \Gamma$.
	We want to show that the constructed $\gamma$ is nondegenerate and nonredundant.
	As $\Gamma$ is nondegenerate, there is some report $r \in \reals^d$ such that $r \in \Gamma(p)$.
	For every $p \in \P$, there is some level set $\theta$ so that $p \in \cl{\theta}$, and since level sets of elicitable properties are closed (see Lemma~\ref{lem:closed-level-sets}), and therefore $p \in \theta$.
	Thus there is some report $r \in \R'$ so that $r \in \gamma(p)$, so $\gamma$ is nondegenerate.

	\jessie{This next paragraph is definitely incomplete (HOLE)}
	If $\gamma$ is redundant, then remove any redundant reports from $\R'$.
	Any level set with a redundant report must either (a.) equal to another level set or (b.) a proper subset of another level set. 
	However, in our preliminary step of removing redundant reports in $\reals^d$ in defining $\R$, we know that (a.) does not happen.
	To see that (b.) does not happen, consider that a level set of an elicitable property is a proper subset 
	\jessie{End the hole here}

@@

\begin{lemma}\label{lem:define-trim}
	Let $\Gamma$  be a nondegenerate, elicitable property with a finite set of level sets $\Theta$ so that $\bigcup_{\theta \in \Theta} \theta = \P$.
	There exists an unlabeled property $\Theta$ so that for all nondegenerate, nonredundant $\gamma \preceq \Gamma$, we have $\strip(\gamma) = \Theta := \trim(\Gamma)$.
\end{lemma}

@@

@@

	We define $\trim(\Gamma)$ in terms of the property $\gamma: \P \toto \R'$ such that $\gamma \preceq \Gamma$ and $\R'$ is as constructed in Conjecture~\ref{conj:gam-prime-exists}.
	For each $\theta \in \trim(\Gamma) = \strip(\gamma)$, there must be a report $r \in \R'$ such that $\theta = \gamma_r = \Gamma_{r}$.
	By construction, $r \in \R' \implies \inter{\gamma_r} = \inter{\theta} \neq \emptyset$.
	Since $\theta$ is convex (as level sets of elicitable properties are) and has nonempty interior, then $\theta$ is full dimensional.

\begin{conjecture}\label{conj:lev-sets-subsets}
	Let the property $\Gamma: \P \toto \reals^d$ be convex elicitable and the nondegenerate, nonredundant property $\gamma: \P \toto \R$ so that $\gamma \preceq \Gamma$.
	Then the level sets of $\Gamma$ are subsets of the level sets of $\gamma$.
	%\jessie{Statement needs to be changed so instead of assuming embedding, just want $\gamma \preceq \Gamma$.}
\end{conjecture}

\begin{proof}
	It is sufficient to show $\theta \in \strip(\Gamma) \implies \theta \in \strip(\gamma)$.
	For every $r \in \reals^d$, there is some $r' \in \R$ so that $ p \in \theta = \Gamma_r = \{ p \in \P : r \in \Gamma(p) \} \subseteq \Gamma_{r'} \implies p \in \Gamma_{r'}$ in two cases.

	First, if $r \not \in \R$, it is a redundant report, so its level set is a subset or equal to another level set for a report in $\R$.
	In the second case, for $r' \in \R$, we know $p \in \Gamma_{r'} \implies p \in \{ p \in \P : r' \in \Gamma(p) \cap \R \} = \{ p \in \P : r' \in \gamma(p) \} = \gamma_{r'}$. 
\end{proof}

\section{Defining Embeddability}

\begin{proposition}\label{prop:optimal-reports-per-level-set}
  Let $\Gamma:\P\toto\reals^d$ be a non-degenerate (convex) elicitable property.

  The following are equivalent:
  \begin{enumerate}
  \item There is a nondegenerate, finite property $\gamma:\P\toto\R'$ and $\R \subseteq \reals^d$ such that there is an injection $\varphi:\R'\to\reals^d$ such that $r\in\gamma(p) \iff \varphi(r) \in \Gamma(p)$. (i.e. $\Gamma$ embeds finite $\gamma$).  
  \item There is a finite set of full dimensional level sets $\Theta$ of $\Gamma$ that union to $\P$.
  \item $\strip(\Gamma)$ is finite.
  \item $\trim(\Gamma)$ is finite.
  \item $\trim(\Gamma)$ is finite and elicitable.
